---
title: "introduction"
author: "Bryan"
date: "`4.27.2018`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(dieroller)
```




## Die rolling

The package `"dieroller"` is a minimal implementation for simulating rolling a die given number of times, and to visualize the relative frequencies in sucha a series of rollings.


## Creating a `die`

The first step is to create a `"die"` object with the function `die()`:

```{r}
mydie <- die()
mydie
```

By default, `die()` creates a _fair_ die with standard sides `1,2,3,4,5,6`, and with probability values for each side 1/6.

You can change the defatuls with arguments `sides` and `prob`:

```{r}
# die with non-standard sides
weird_die <- die(sides = c('i', 'ii', 'iii', 'iv', 'v', 'vi')) 
weird_die

# create a loaded die
loaded_die <- die(prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
loaded_die
```


## Rolling a die

Once you have defined a `"die"` object, you can use the function `roll()` to
_roll_ a coin a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `rolls`:

```{r}
roll20 <- roll(mydie, times = 20)
roll20
```

The `summary()` function gives you a nice table of frequencies:
```{r}
summary(roll20)
```


## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of coin tosses:

```{r, fig.show='hold'}
plot(roll20)
```
